### 2018-05-10 Paper/examples.tex
..

Our goal as discussed is to gain computational advantage by constructing
surrogates in a reduced input parameter space. To this end, we construct PCE's
in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
fixing $K_w$ in the latter at their respective mean values. In
Figure~\ref{fig:conv_bore}, we compare convergence of PCE's constructed in the
full space (7D) with those constructed in the two reduced spaces (4D and 5D)
using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/err_samples_borehole}
\caption{A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \alennote{Use different line styles
and colors. Also use thicker lines. Instead of taking log of the error, just use a 
semilogy in Matlab to use logarithmic scale on the y-axis.}}
\label{fig:conv_bore}
\end{center}
\end{figure}

@@

Figure~\ref{fig:pdfcomp_bore} illustrates a comparison of the PDF's of the
discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ Monte-Carlo (MC)
samples through the 7D PCE in the original input parameter domain as well as
the reduced order PCE's constructed in 4 and 5 dimensions. 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
by propagating
parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
were obtained using 10$^{6}$ MC samples in the input parameter domain.
\alennote{Use thicker lines, different colors in addition to line styles, larger 
font size, and also use the x-axis limits to be $[0, 300]$, maybe? 
Once figures 4, 5 are appropriate reformatted, I would combine them in one line as I did 
things in figure 2.}
} 
\label{fig:pdfcomp_bore}
\end{center}
\end{figure}
It is evident from this plot, that the PDF's agree quite favorably with each
other. Consequently, it can be said that the reduced order PCE is verified in a
probabilistic sense. In other words, the mode as well as the uncertainty in the
observable is reliably captured and predicted by the reduced order PCE.

>>>>

Our goal as discussed is to gain computational advantage by constructing
surrogates in a reduced input parameter space. To this end, we construct PCE's
in 5D and 4D spaces by fixing $\{T_u,T_l\}$ in the former and additionally
fixing $K_w$ in the latter at their respective mean values. In
Figure~\ref{fig:conv_bore}(left), we compare convergence of PCE's constructed in the
full space (7D) with those constructed in the two reduced spaces (4D and 5D)
using $\epsilon_{\mbox{\tiny{LOO}}}$ (Eq.~\ref{eq:loo}). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_borehole}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_borehole}
\caption{Left: A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. Right: A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}

@@

Figure~\ref{fig:conv_bore}(right) illustrates a comparison of the PDFs
of the
discharge, $\mathcal{Q}$ obtained by propagating 10$^6$ random
samples through the 7D PCE in the original input parameter domain as well as
the reduced order PCEs constructed in 4 and 5 dimensions. 
%\begin{figure}[htbp]
% \begin{center}
%  \includegraphics[width=0.6\textwidth]{./Figures/pdf_comp_borehole}
%\caption{A comparison of PDF's of the discharge, $\mathcal{Q}$ as obtained
%by propagating
%parametric uncertainties through the 4D, 5D, and 7D PCE's.These PDF's 
%were obtained using 10$^{6}$ MC samples in the input parameter domain.} 
%\label{fig:pdfcomp_bore}
%\end{center}
%\end{figure}
It is evident from this plot, that the PDFs agree quite favorably with each
other with respect to the modal estimate as well as the uncertainty associated with 
$\mathcal{Q}$. 
Consequently, it can be said that the reduced order PCE is verified in a
probabilistic sense. In other words, the mode as well as the uncertainty in the
observable is reliably captured and predicted by the reduced order PCE.
